Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-04-30 paper/paper.tex
fix picture

Participants were seated in a comfortable position facing the laptop screen. They were instructed to follow a series of calibration points displayed on the screen to calibrate the eye-tracking system. This calibration process ensured accurate measurement of eye movements during the subsequent tasks.

During the cognitive task component of the study, participants performed a quantified behavioral test (QBTest) while their eye movements were tracked by the EyeWriter 2.0 camera mounted on the laptop. The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
% Further details on the cognitive task will be provided in subsequent sections. They will then move on the the QBTest?. % This will need to be re-written.

\subsection[short]{Participants}
Approximately twenty participants were recruited from Colorado State University. Ten males and ten females all in the age range of 18-99. There were no %chktex 8
restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
They have all previously either learned to type at primary school or through necessity.

\subsection[short]{Equipment}  % Do we want to change this to Equipment? 
% This may not need to be broken into subsections. Will decide before we resubmit. 
Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 14. One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it. The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test.

QBTest MacBook Pro with Eye Tracker: This MacBook Pro was dedicated to conducting the QBTest. It had the eye tracker mounted on it, which made it difficult to access the keyboard for typing. Participants used this MacBook Pro for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test.

@@

\subsubsection{EyeWriter 2.0}
The IR camera captures the eye movements of the participant.
It is mounted on the laptop that participants use for the QBTest, allowing for the tracking of eye movements during the test.
IR LEDs are used to illuminate the eye to enhance the visibility of the eye for tracking purposes. 
These LEDs are also mounted on the laptop along with the IR camera. 
The mounting system holds the IR camera and IR LEDs in place relative to the participant's eye. 
It ensures that the camera has a clear view of the eye for accurate tracking. 
Cables are used to connect the IR camera and IR LEDs to the laptop. These cables transmit data and power between the components.
% \subsubsection{QB Test} 
\subsubsection{Typing Test}
The typing program was written in Python and compiled using Python3.9. While python can run on any device that has python installed, this study only used the two Macbook Pros. The singularity of the devices was used as the center of the screen for the typing test was hard coded when setting the starting position of the window for the typing test.

@@

\subsection[short]{Procedure}
After signing consent forms, each participant was explained the overall concept of what they would be doing. First they would take the short typing test three times to account for the three levels of music.

>>>>

Participants were seated in a comfortable position facing the laptop screen. The laptop is placed on top of a laptop stand while the eye tracker
is mounted on a wooden frame. While the eye tracker is on a moveable slider, it is centered in front of the screen. At the ends of the wooden
frame are infrared lights that flashes at sixty frames per second. % will need to verify that it is 60 fps.
Although not pictured, a bluetooth keyboard is used by the participant for the quantified behavioral test (QB test).

\begin{figure}
  \includegraphics[width=0.3\textwidth]{eyetracker_setup.png}
  \caption{EyeWriter 2.0}
  \Description{Image of the eye tracker setup}
\end{figure}

During the cognitive task component of the study, participants performed a QB test while their eye movements were tracked by the EyeWriter 2.0. The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
% Further details on the cognitive task will be provided in subsequent sections. They will then move on the the QBTest?. % This will need to be re-written.

\subsection[short]{Participants}
Approximately eight participants were recruited from Colorado State University. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
They have all previously either learned to type at primary school or through necessity.

\subsection[short]{Equipment} 
% This may not need to be broken into subsections. Will decide before we resubmit. 
Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 14. One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it. The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test and QB test.

QBTest MacBook Pro with Eye Tracker: This MacBook Pro was dedicated to conducting the QBTest. It had the eye tracker mounted on it, which made it difficult to access the keyboard for typing. Participants used this MacBook Pro for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test. A bluetooth keyboard was used as part of the QB test since the positioning of the Eye Writer mostly blocked the space bar.

@@

\subsubsection{EyeWriter 2.0}
The IR camera captures the eye movements of the participant.
It is mounted on the laptop that participants use for the QBTest, allowing for the tracking of eye movements during the test.
IR LEDs are used to illuminate the eye to enhance the visibility of the eye for tracking purposes. 
These LEDs are also mounted on the laptop along with the IR camera. 
The mounting system holds the IR camera and IR LEDs in place relative to the participant's eye. 
It ensures that the camera has a clear view of the eye for accurate tracking. 
Cables are used to connect the IR camera and IR LEDs to the laptop. These cables transmit data and power between the components.
An Arduino microcontroller allowed the computer to communicate with the camera, infrared LED lights, and computer.
% \subsubsection{QB Test} 
\subsubsection{Typing Test}
The typing program was written in Python and compiled using Python3.9. While python can run on any device that has python installed, this study only used the two Macbook Pros. The singularity of the devices was used as the center of the screen for the typing test was hard coded when setting the starting position of the window for the typing test.

@@

\subsection[short]{Procedure}
After signing consent forms, each participant was explained the overall concept of what they would be doing. First they would take the short typing test three times to account for the three levels of music. They would then do a QB test three times again for the music. The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.
